ROV report

### 2020-03-23 analysis/reports/rov.Rmd
rarefaction

eighty_smallest <- filter(all_di, log_nparts <= 8.6)
mean(eighty_smallest$skew_percentile >= 95)

twenty_largest <- filter(all_di, log_nparts >= 8.6)
mean(twenty_largest$skew_percentile >= 95)

@@

>>>>

eighty_smallest <- filter(all_di, log_nparts <= 8.6)
mean(eighty_smallest$skew_percentile >= 95)
mean(eighty_smallest$simpson_percentile <= 5)

twenty_largest <- filter(all_di, log_nparts >= 8.6)
mean(twenty_largest$skew_percentile >= 95)
mean(twenty_largest$simpson_percentile <= 5)

@@

```{r rarefaction stats}
# proportion of %iles above 95/below 5
# skew
mean(all_di_singletons$skew_percentile >= 95)
# simpson
mean(all_di_singletons$simpson_percentile <= 5)

nparts_summary2 <- all_di_singletons %>%
  group_by(qbinned_lognparts) %>%
  summarize(high_skew = mean(skew_percentile >= 95),
            low_simpson = mean(simpson_percentile <= 5)) %>%
  ungroup()

nparts_summary2
